Joint estimation of ancestral states and phylogenetic model parameters is inconsistent

### 2017-11-14 joint_inf.tex
update caption and add description

Define $\ell_{\tau^*,t^*}(\tau, t; \fullAncestralSplitPartitions(\tau,t))$ as
$$
\frac{1}{n}\log L_\nCols'(\tau, t; \fullAlignment) \rightarrow \ell_{\tau^*,t^*}(\tau, t; \fullAncestralSplitPartitions(\tau,t)).
$$
We show the following.
\begin{theorem}
There exist $L_0$ and $L_1$ such that
$$
\max_{t} \ \ell_{\tau_1,t^*}(\tau_1, t; \fullAncestralSplitPartitions(\tau_1,t)) \le L_0,
$$
$$
\max_{t} \ \ell_{\tau_1,t^*}(\tau_2, t; \fullAncestralSplitPartitions(\tau_2,t)) \ge L_1
$$
and $L_1 > L_0$.
\end{theorem}

@@

\begin{figure}
\centering
% obtained by running
% python joint_inf_plot.py --empirical --general-branch-lengths --delta .001 --plot-name figures/w-hat-empirical-001.svg --pkl-name figures/w-hat-empirical-001.pkl --n-jobs 16
% or
% python joint_inf_plot.py --empirical --general-branch-lengths --plot-name figures/w-hat-empirical-001.svg --in-pkl-name figures/w-hat-empirical-001.pkl
% if fit already
\includegraphics[width=.9\textwidth]{w-hat-empirical-001}
\caption{
    %das: note to update caption
    Estimating $(\hat{x}', \hat{y}', \hat{w}')$.
}
\label{fig:bl-general-inconsistency}
\end{figure}

>>>>

Define $\ell_{\tau^*,t^*}(\tau, t; \fullAncestralSplitPartitions(\tau,t))$ as
$$
\frac{1}{n}\log L_\nCols'(\tau, t; \fullAlignment) \rightarrow \ell_{\tau^*,t^*}(\tau, t; \fullAncestralSplitPartitions(\tau,t)).
$$
We show the following.
\begin{theorem}
There exist $L_0(x, y)$ and $L_1(x, y)$ such that
$$
\max_{t} \ \ell_{\tau_1,t^*}(\tau_1, t; \fullAncestralSplitPartitions(\tau_1,t)) \le L_0(x, y),
$$
$$
\max_{t} \ \ell_{\tau_1,t^*}(\tau_2, t; \fullAncestralSplitPartitions(\tau_2,t)) \ge L_1(x, y)
$$
and $L_1(x, y) > L_0(x, y)$.
\end{theorem}
Fig.~\ref{fig:inconsistency-farris} shows the region where $L_1(x, y) > L_0(x, y)$.

@@

\begin{figure}
\centering
% obtained by running
% python joint_inf_plot.py --empirical --general-branch-lengths --delta .001 --plot-name figures/w-hat-empirical-001.svg --pkl-name figures/w-hat-empirical-001.pkl --n-jobs 16
% or
% python joint_inf_plot.py --empirical --general-branch-lengths --plot-name figures/w-hat-empirical-001.svg --in-pkl-name figures/w-hat-empirical-001.pkl
% if fit already
\includegraphics[width=.9\textwidth]{w-hat-empirical-001}
\caption{
    %das: note to update caption
    Region where $\hat{w}'=1$ computing empirical estimates of $(\hat{x}', \hat{y}', \hat{w}')$.
}
\label{fig:bl-general-inconsistency}
\end{figure}
